\documentclass{resume}
\usepackage[hidelinks]{hyperref}
\usepackage{lipsum}

\name{Patrick Earl}
\contact{\href{tel:+1 484-903-7150}{+1 484-903-7150}}
\contact{\href{mailto:patrick.earl95@gmail.com}{patrick.earl95@gmail.com}}
\contact{\href{https://www.pat-earl.com}{www.pat-earl.com}}
\contact{Allentown, PA}

\begin{document}
\makeheader

\begin{ResumeSection}{experience}
    \begin{ResumeSubsection}{org={Kutztown University of PA}, location={Kutztown, PA}, position={Instructor}, duration={08/2019 - Present}}
        \begin{itemize}
            \item Facilitate and deliver lectures for undergraduate computer science courses. Primary topics taught include: 
            \begin{itemize}
                \item Computer Science I (taught using C++)
                \item Data Analysis using Python \& Pandas
                \item Data Visualization with Tableau
                \item Computer Networks (Focus on App-Layer Protocols and overview of TCP/IP Reference Layers)
                \item Linux (Filesystem Overview, Basic Commands, Processes, Text Processing, Scripting)
                \item Computing Systems Integration
            \end{itemize}
            \item Serve on departmental and university-wide committees.
            \item Maintain various PHP web applications used by the CS\&IT Department.
        \end{itemize}
    \end{ResumeSubsection}    
    \begin{ResumeSubsection}{org={Kutztown University of PA}, location={Kutztown, PA}, position={Graduate Assistant}, duration={08/2018 - 05/2019}}
        \begin{itemize}
            \item Assisted with data collection for an \emph{NSF} grant.
            \item Held tutoring hours for undergraduate computer science students. 
        \end{itemize}
    \end{ResumeSubsection}
    \begin{ResumeSubsection}{org={St. Lukes University Health Network}, location={Allentown, PA}, position={Data Reporting Internship}, duration={05/2018 - 08/2018}}
        \begin{itemize}
            \item Improved and added features to an existing \textbf{Python} application used to verify links between records in vendor-specific databases. 
            \item Created \textbf{Python} selenium script used to automate downloading of CSV files from a web application.
        \end{itemize}
    \end{ResumeSubsection}
\end{ResumeSection}

\begin{ResumeSection}{skills}
    \newcommand{\skill}[2]{\textbf{#1} - #2}
    \begin{ResumeSubsection}{org=Technical}
        \begin{itemize}
            \item \skill{Programming Languages}{Python, C++}
            \item \skill{Computer Networking}{DNS, HTTP, Routing, TCP/IP Reference Model}
            \item \skill{Linux System Administration}{BASH Scripting, Management, Software Installations}
        \end{itemize}
    \end{ResumeSubsection}
\end{ResumeSection}

\begin{ResumeSection}{education}
    \begin{ResumeSubsection}{org={Kutztown University of PA}}
        \begin{itemize}
            \item Data Analytics Graduate Certificate \hfill Dec. 2020
            \item Master of Science (Computer Science) \hfill May 2019
            \begin{itemize}
                \item Focus: \emph{Computer Networks}
            \end{itemize}
            \item Bachelor of Science (Computer Science) \hfill May 2018
        \end{itemize}
    \end{ResumeSubsection}
\end{ResumeSection}

\begin{ResumeSection}{projects}
    \begin{ResumeSubsection}{org={Kutztown University}}
        \begin{itemize}
            \item Collaborated with University IT department on various projects to improve student learning. 
            \item Helped craft grant proposal for NSF \emph{CS4All} grant which was accepted early 2021,
            with the focus on developing a CS curriculum framework to introduce K-12 students to CS topics.  
            Will be serving on the advisory board and help with running and leading workshops for 6 days 
            in 2022-2023. 
        \end{itemize}
    \end{ResumeSubsection}
    \begin{ResumeSubsection}{org={KU - Graduate Studies}}
        \begin{itemize}
            \item Graduate Group Project which focused on designing a computer network for a fictional university. Group was tasked with 
            selecting equipment, creating network room layouts, and subnetting our allocated IP block. 
            \item Developed distributed chat server for Linux using \textbf{C++} with a multi-process server that kept client records in shared memory.
        \end{itemize}
    \end{ResumeSubsection}
\end{ResumeSection}

\end{document}
